---
title: "Bruce Kimbark Unit 04 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 538 Data
a
##### In R: install.packages("fivethirtyeight")
b
```{r}
data(package = "fivethirtyeight")
setwd("C:\\Users\\bpkim\\OneDrive\\Desktop\\6306DoingDataScience\\SMUMSDSHomework") #To makes sure I am placeing the rmd and html files where I can push them to GitHub. This is the location I have synched my desktop to the repository.
df <- fivethirtyeight::college_recent_grads
```
c
For a detailed list of all the data sets, the data and descriptions are housed in the following address: https://github.com/rudeboybert/fivethirtyeight/tree/master/data

The College Recent Grads file can be found here: fivethirtyeight/data/college_recent_grads.rda 

As indicated in their ReadMe file, 
To see a more detailed list of all data sets, see the package vignette:
vignette("fivethirtyeight", package = "fivethirtyeight")

d
```{r}
str(df) #to give dimension and column names together
```

##Question 2 Data Summary
a
```{r}
colnames(df) #names of the columnns
ncol(df) #number of columnns
```
b
```{r}
major_count <- table(df$major_category) #creating an object based on Major Categories
```
c
```{r}
par(las=2)
barplot(major_count, #Creating a bar plot
        main= "Nmber of Students Graduating per Major Categories",
        xlab = "College Major",
        ylab = "Number of Students",
        col = "steelblue3",
        horiz = TRUE)
```

d
```{r}
write.csv(df, file = "Recent_College_Grads.csv", row.names=FALSE) #Saving the CSV to the local repo
```

##Question 3
a
```{r}

```